Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2022-10-18 src/tex/intro.tex
finish toms comments

Observations of gravitational waves (GWs) from compact binary mergers are becoming a regular occurrence, 
producing a catalog of events that recently surpassed 90 such detections \citep{GWTC1,gwtc2,GWTC3}. As the catalog continues to grow, so does our understanding of the underlying astrophysical population of compact binaries \citep{o1o2_pop,o3a_pop,o3b_astro_dist}. 
Following numerous improvements to the detectors since the last observing run, the anticipated sensitivities for the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration suggest detection rates as high as once per \emph{day} \citep{aLIGO,aVIRGO,LVK_prospects}. With the formation history of these dense objects encoded in the details of their distribution \citep{Zevin_2017}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics. 
Beyond formation physics, population-level inference of the compact binary catalog has also been shown to provide novel measurements of cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo,JoseSpectralSirens}, constrain modified gravitational wave propagation \citep{OkounkovaBirefringence,ModGWProp,ModGWProp2}, 
constrain a running Planck mass \citep{Lagos_runningPlanckMass}, search for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, 
and to constrain physics of neutron stars \citep{Golomb_EOS,LandryRead_NS_Masses2021}. Through a better understanding of the mass, spin, and redshift distributions of 
compact binaries that will come with the increased catalog size, one can probe a wide range of different physical phenomena with even greater fidelity.

>>>>

Observations of gravitational waves (GWs) from compact binary mergers are becoming a regular occurrence, 
producing a catalog of events that recently surpassed 90 such detections \citep{GWTC1,gwtc2,GWTC3}. As the catalog continues to grow, so does our understanding of the underlying astrophysical population of compact binaries \citep{o1o2_pop,o3a_pop,o3b_astro_dist}. 
Following numerous improvements to the detectors since the last observing run, the anticipated sensitivities for the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration suggest detection rates as high as once per \emph{day} \citep{aLIGO,aVIRGO,LVK_prospects,KAGRAProg}. With the formation history of these dense objects encoded in the details of their distribution \citep{Zevin_2017}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics. 
Beyond formation physics, population-level inference of the compact binary catalog has also been shown to provide novel measurements of cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo,JoseSpectralSirens}, constrain modified gravitational wave propagation \citep{OkounkovaBirefringence,ModGWProp,ModGWProp2}, 
constrain a running Planck mass \citep{Lagos_runningPlanckMass}, search for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, 
and to constrain physics of neutron stars \citep{Golomb_EOS,LandryRead_NS_Masses2021}. Through a better understanding of the mass, spin, and redshift distributions of 
compact binaries that will come with the increased catalog size, one can probe a wide range of different physical phenomena with even greater fidelity.
